VOCC outline

### 2020-04-15 ms/ms.Rmd
more draft fig captions

@@

dogfish - increasing DO and warming both bad
pacific cod - 
English - warming neutral when cool, bad when warm
Arrowtooth or Dover - warming good when it's cool, neutral when warm 
sablefish - warming good, increasing DO not

@@

```{r temp-chops, fig.cap="Temperature ...", out.width="6in"}
# include_graphics(here("ms", "figs", "temp-chops.pdf"))
```

```{r do-chops, fig.cap="Dissolved oxygen ...", out.width="6in"}
# include_graphics(here("ms", "figs", "do-chops.pdf"))
```

```{r slope-by-depth, fig.cap="Variation in slopes across species with different mean depths of occurrence.", out.width="4in"}
include_graphics(here("ms", "figs", "slope-by-depth.pdf"))
```

<!-- TODO: May be we should change this to mean age of mature fish sampled for each species? That would make it easier to relate values to the timespan of the study. 
-->

```{r coef-by-max-age.pdf, fig.cap="The maximum lifespan of the species may influence the relationships between climate trends and biomass change.", out.width="4in"}
include_graphics(here("ms", "figs", "coef-by-max-age.pdf"))
```

@@

Supplemental figures:
(In no particular order)
-   flow diagram
-   spatial residuals
-   null model stuff

-   all the chopstick panels both trend and velocity

<!-- TODO: change orientation to landscape? -->

@@

@@

-   other coefs plot
<!-- TODO: This fig might go here instead of in results -->

```{r supp-coef-scatterplots, fig.cap="Caption goes here", out.width="6in"}
include_graphics(here("ms", "figs", "supp-coef-scatterplots.pdf"))
```

-   pairs plot of predictors

-   plot vocc regression residuals against the main predictors... (and not in model and fitted vs. residuals plot; but don't necessarily include in paper)

```{r yet-another, fig.cap="Caption goes here", out.width="5in"}
include_graphics(here("ms", "figs", "example.pdf"))
```

>>>>

<!-- TODO: can a % symbol be used in fig caption? -->

@@

dogfish - increasing DO and warming both bad
pacific cod - 
English - warming neutral when cool, bad when warm
Dover - warming good when it's cool, neutral when warm  
(arrowtooth shows similar pattern but likely influenced strongly by fishing... could include for that reason though?)

sablefish - warming good, increasing DO not

@@

```{r temp-chops, fig.cap="Temperature ...", out.width="10in"}
include_graphics(here("ms", "figs", "temp-chops.pdf"))
```

```{r do-chops, fig.cap="Dissolved oxygen ...", out.width="6in"}
include_graphics(here("ms", "figs", "do-chops.pdf"))
```

```{r coef-scatterplots, fig.cap="Main effect coefficients for relationship between biotic trends and changes in climate for species with different life history strategies. Mean age and depth are calculated across all sampled individuals of each maturity class (as defined by the length at 50 percent maturity threshold) within a species. Growth rate is estimated as the length at maturity for females divide by the 0.95 quantile of ages recorded for immatures of each species.", out.width="9in"}
include_graphics(here("ms", "figs", "coef-scatterplots.pdf"))
```

@@

Supplemental figures:
(not yet done)
-   flow diagram
-   spatial residuals
-   null model stuff
-   pairs plot of predictors
-   plot vocc regression residuals against the main predictors... (and not in model and fitted vs. residuals plot; but don't necessarily include in paper)

@@

```{r supp-coef-scatterplots, fig.cap="Differences slope of effect of climate change on biotic change at how high and low mean conditions (columns) plotted against species life histories. Simple regression lines plotted for immature abundance only. Mean age and depth are calculated across all sampled individuals of each maturity class (as defined by the length at 50 percent maturity threshold) within a species. Growth rate is estimated as the length at maturity for females divide by the 0.95 quantile of ages recorded for immatures of each species.", out.width="8in"}
include_graphics(here("ms", "figs", "supp-slope-scatterplots.pdf"))
```

@@

```{r supp-slope-by-depth, fig.cap="Shape of relationship between estimated mean dissolved oxygen and mean depth of each 4x4 km grid cell (pattern is vary similar for temperature so not illustrated) for comparison with slopes for the environmental extremes experienced at the deeper depths showing expected tendancy towards increasing variation in strength of responses amongst species with deeper mean depth of occurrence. Outliers amongst immatures are Widow Rockfish (both DO and temperature) and Bocaccio (temperature).", out.width="4in"}
include_graphics(here("ms", "figs", "supp-slope-by-depth.pdf"))
```
